%----------------------------------------------------------------------------------------
%	Document Definition
%----------------------------------------------------------------------------------------

\documentclass[a4paper,10pt]{article}

%----------------------------------------------------------------------------------------
%	Font
%----------------------------------------------------------------------------------------

% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	Packages
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

% Other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

% Tabularx environment
\usepackage{tabularx}

% For lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

% To prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

% Custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{5pt}{5pt}

% For publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colors for links
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\usepackage[
    pdfauthor={Mohamed Tahiri},
    pdftitle={CV - Mohamed Tahiri},
    pdfsubject={CV of Mohamed Tahiri},
    pdfkeywords={Mohamed Tahiri, CV, Resume},
    colorlinks,
    breaklinks,
    urlcolor=linkcolour,
    linkcolor=linkcolour
]{hyperref}

\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}


% job listing environments
\newenvironment{jobshort}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    } {}


\newenvironment{joblong}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]
    }
    {
    \end{itemize}
    \end{minipage}    
    }



%----------------------------------------------------------------------------------------
%	Begin Document
%----------------------------------------------------------------------------------------
\begin{document}

% Non-numbered pages
\pagestyle{empty}

%----------------------------------------------------------------------------------------
%	Header
%----------------------------------------------------------------------------------------

\begin{tabularx}{\linewidth}{@{} C @{}}
    \Huge{Mohamed Tahiri}                                                                 \\[7.5pt]
    \href{https://mohamedtahiri.com}{\raisebox{-0.05\height}\faGlobe \ mohamedtahiri.com} \\
\end{tabularx}

\begin{tabularx}{\linewidth}{@{} C @{}}
    \href{https://github.com/moha-tah}{\raisebox{-0.05\height}\faGithub\ @moha-tah} \ $|$ \
    \href{https://linkedin.com/in/moha-tah}{\raisebox{-0.05\height}\faLinkedin\ moha-tah} \ $|$ \
    \href{mailto:me@mohamedtahiri.com}{\raisebox{-0.05\height}\faEnvelope \ me@mohamedtahiri.com} \ $|$ \
    \href{tel:+33768442555}{\raisebox{-0.05\height}\faMobile \ +33 7 68 44 25 55} \\
\end{tabularx}

% \section{Summary}
Software Engineering student at UTC specializing in Computer Systems, seeking a 6-month internship from February 2026, passionate about designing efficient architectures and building intelligent, high-performance applications.

%----------------------------------------------------------------------------------------
%	Body
%----------------------------------------------------------------------------------------

\section{Work Experience}

% \begin{joblong}{Freelance Full Stack Developer}{April 2024 - Present}
%     \item line
%     \item line
% \end{joblong}

\begin{joblong}{Software Engineer Intern, \href{https://www.napta.io}{Napta}, Paris}{Sept. 2024 - Feb. 2025}
    \item \textbf{Data Engineering \& Automation} – Built and optimized ETL pipelines using Python and Airflow for APIs, SFTP, databases, CSV files etc., handling large-scale data processing (millions of rows).
    \item \textbf{Backend and Frontend Development} – Enhanced internal Flask tools, contributed to React/Next.js projects, and built a GitLab-to-Slack integration cutting PR review time by 50\%.
    \item \textbf{Collaboration \& Impact} – Worked cross-functionally with code reviews, testing, and coordination with Account Managers, enhancing team efficiency and technical versatility (DevOps/CI-CD included).
\end{joblong}

\begin{jobshort}{Competitive Programming Club Teacher, \href{https://www.utc.fr}{UTC}, Compiègne}{Feb. 2024 - Feb. 2025}
    Trained other students for algorithm and data structure-based competitions. Participated in university-level competitions as a member of this association. Achieved a 6th place out of over 50 teams in a competition organized by Sopra Steria.
\end{jobshort}

\begin{jobshort}{Intern, \href{https://www.loreal.com}{L'Oréal}, Paris}{Jan. 2023 - Feb. 2023}
    Applied technical skills to optimize order picking processes and improve workflow efficiency. Collaborated with team members to streamline inventory management and meet high throughput rates.
\end{jobshort}

% Projects
\section{Projects}

\begin{joblong}{Course Search Engine – SaaS Web Application}{\href{https://mohamedtahiri.com/projects/my-biggest-project}{Learn more}}
    \item Developed a SaaS course search engine with Next.js, NestJS, PostgreSQL, Supabase, AWS, and Algolia (AI-powered filtering \& ranking engine) with 6 engineers. Release in October 2025.
    \item Implemented secure backend features: JWT authentication, role-based access control, CI/CD pipelines (GitHub Actions).
    \item Built real-time chat, student/teacher dashboards, tests with Jest and scalable environments (dev, preview, prod).
\end{joblong}

\begin{joblong}{My Portfolio – \href{https://mohamedtahiri.com}{mohamedtahiri.com}}{\href{https://github.com/moha-tah/portfolio}{See code}}
    \item Built the frontend in Next.js with Tailwind CSS, i18n and TanStack Query, and the backend in NestJS with PrismaORM and Swagger for API documentation.
    \item Set up CI/CD with GitHub Actions (automated translations, testing and deployment) and deployed on Vercel (frontend) and Railway (backend).
\end{joblong}

\begin{jobshort}{Sumo Spheres – Online Multiplayer Game}{\href{https://mohamedtahiri.com/projects/online-multiplayer-game}{Learn more}}
    Built an arena game (Windows/Mac) with real-time physics, AI-driven opponents, and online mode using Unity Cloud. Engineered real-time networking with sockets, UDP/TCP optimization and $<$200ms latency for up to 10 players.
\end{jobshort}

\begin{jobshort}{Decentralized Distributed System}{\href{https://mohamedtahiri.com/projects/decentralized-distributed-system}{Learn more}}
    Designed a fully decentralized distributed system where nodes collect, verify, and share sensor data, ensuring consistency with logical clocks, election algorithms, and peer-to-peer coordination.
\end{jobshort}

%----------------------------------------------------------------------------------------
%	Education
%----------------------------------------------------------------------------------------
\section{Education}

\begin{jobshort}{2021 - 2026    Software Engineering Master's Degree, \href{https://www.utc.fr}{UTC}, France}{GPA: 3.6/4.0}
    Specialized in Computer Systems Engineering. \textbf{Main courses:} Algorithms \& Data Structures, OOP, Computer Architecture, OS, Networks, Cybersecurity, Web Development, etc.
\end{jobshort}

\begin{jobshort}{2018 - 2021    Private High School, L'Espérance, France}{Diploma with Highest Honors}
\end{jobshort}

%----------------------------------------------------------------------------------------
%	Skills
%----------------------------------------------------------------------------------------
\section{Skills}

\begin{tabularx}{\linewidth}{@{}l X@{}}
    \textbf{Backend}             & \normalsize{Python, TypeScript, NestJS, TypeORM, Prisma, Flask, SQL, Airflow, Java}                     \\
    \textbf{Frontend}            & \normalsize{React, Next.js, Tailwind CSS, Vite, Figma}                                                  \\
    \textbf{DevOps}              & \normalsize{Cloudflare, Vercel, AWS, GCP, GitHub Actions, GitLab CI/CD, Shell, Turborepo, Jest, Pytest} \\
    \textbf{Automation/AI Tools} & \normalsize{Zapier, Make, Google Apps Script, Claude Code, Cursor, OpenAI API}                          \\
    \textbf{Languages}           & \normalsize{French (Native Language), English (C1 Level, TOEIC 985)}                                    \\
\end{tabularx}

\end{document}
